Identifying regime transitions for water governance at a basin scale

### 2021-03-04 tex/main/manuscript.tex
Rectified by Cumming's comments.

% PNAS研究论文模板
\templatetype{pnasresearcharticle} % Choose template 
% {pnasresearcharticle} = Template for a two-column research article
% {pnasmathematics} %= Template for a one-column mathematics article
% {pnasinvited} %= Template for a PNAS invited submission
% \usepackage{cite}
\usepackage{url}	
% 文章标题：“流域尺度的水资源利用体系：过渡框架和发展困局”
\title{Identifying regime transitions for water governance at a basin scale}
\label{title}
% Use letters for affiliations, numbers to show equal authorship (if applicable) and to indicate the corresponding author
% 作者列表
\author[a, b]{Shuang Song}  % 宋爽，一作
\author[a, b]{Shuai Wang}  % 王老师，通讯
\author[c, d]{Xutong Wu}  % 武旭同
\author[e]{Yongping Wei} % 尉老师
\author{Graeme S. Cumming} % Cumming
\author[a, b, 1]{Bojie Fu}  % 傅老师

% 机构列表
\affil[a]{ % 北师大地表国重
	State Key Laboratory of Earth Surface Processes and Resource Ecology, 
	Faculty of Geographical Science, 
	Beijing Normal University, 
	Beijing 100875, 
	P.R. China
}
\affil[b]{ % 北师大地理学部
	Institute of Land Surface System and Sustainability, 
	Faculty of Geographical Science, 
	Beijing Normal University, 
	Beijing 100875, 
	P.R. China
}
\affil[c]{ % 北大城环
	College of Urban and Environmental Sciences, 
	Peking University, 
	Beijing 100871, 
	P.R. China
}
\affil[d]{ % 中科院生态中心
	State Key Laboratory of Urban and Regional Ecology, 
	Research Center for Eco-Environmental Sciences, 
	Chinese Academy of Sciences, 
	Beijing 100085, 
	P.R. China 
}
\affil[e]{ % 昆士兰大学
	School of Earth and Environmental Sciences, 
	The University of Queensland, 
	Brisbane 4067, 
	Australia
}

@@

% 用水关系的变化
The efficiency of water use changed from P2 to P3. While irrigated area resumed its expansion again in P3 (Figure\ref{fig:Causes}A), industry and urban services assumed a stronger economic role (represented by Gross Added Values, GVA) (Figure~\ref{fig:Causes}B). 
However, because of more efficient technology and better water conservation practices (\textit{SI Appendix} Fig. S4), However, because of more efficient technology and better water conservation practices (Figure~\ref{fig:Causes}A and Figure~\ref{fig:Causes}B). 
As a result, the differences between sectors of water use were reduced while the total water consumption remained stable during P3 (\textit{SI Appendix} Fig. S3).

@@

\acknow{Please include your acknowledgments here, set in a single paragraph. Please do not include any acknowledgments in the Supporting Information, or anywhere else in the manuscript.}

>>>>

% PNAS研究论文模板
\templatetype{pnasresearcharticle} % Choose template 
% {pnasresearcharticle} = Template for a two-column research article
% {pnasmathematics} %= Template for a one-column mathematics article
% {pnasinvited} %= Template for a PNAS invited submission
% \usepackage{cite}
\usepackage{url}	
% 文章标题：“流域尺度的水资源利用体系：过渡框架和发展困局”
\title{Identifying regime transitions for water governance at a basin scale}
\label{title}
% Use letters for affiliations, numbers to show equal authorship (if applicable) and to indicate the corresponding author
% 作者列表
\author[a, b]{Shuang Song}  % 宋爽，一作
\author[a, b]{Shuai Wang}  % 王老师，通讯
\author[c, d]{Xutong Wu}  % 武旭同
\author[e]{Yongping Wei} % 尉老师
\author[f]{Graeme S. Cumming} % Cumming
\author[a, b, 1]{Bojie Fu}  % 傅老师

% 机构列表
\affil[a]{ % 北师大地表国重
	State Key Laboratory of Earth Surface Processes and Resource Ecology, 
	Faculty of Geographical Science, 
	Beijing Normal University, 
	Beijing 100875, 
	P.R. China
}
\affil[b]{ % 北师大地理学部
	Institute of Land Surface System and Sustainability, 
	Faculty of Geographical Science, 
	Beijing Normal University, 
	Beijing 100875, 
	P.R. China
}
\affil[c]{ % 北大城环
	College of Urban and Environmental Sciences, 
	Peking University, 
	Beijing 100871, 
	P.R. China
}
\affil[d]{ % 中科院生态中心
	State Key Laboratory of Urban and Regional Ecology, 
	Research Center for Eco-Environmental Sciences, 
	Chinese Academy of Sciences, 
	Beijing 100085, 
	P.R. China 
}
\affil[e]{ % 昆士兰大学
	School of Earth and Environmental Sciences, 
	The University of Queensland, 
	Brisbane 4067, 
	Australia
}
\affil[f]{
	ARC Centre of Excellence for Coral Reef Studies, 
	James Cook University, 
	Townsville 4811, 
	QLD, Australia
}

@@

% 用水关系的变化
The efficiency of water use changed from P2 to P3. While irrigated area resumed its expansion again in P3 (Figure\ref{fig:Causes}A), industry and urban services assumed a stronger economic role (represented by Gross Added Values, GVA) (Figure~\ref{fig:Causes}B). 
However, because of more efficient technology and better water conservation practices (\textit{SI Appendix} Fig. S4), both experienced significant declines in water use for unit production (Figure~\ref{fig:Causes}A and Figure~\ref{fig:Causes}B). 
As a result, the differences between sectors of water use were reduced while the total water consumption remained stable during P3 (\textit{SI Appendix} Fig. S3).

@@

\acknow{Funding was provided by the National Natural Science Foundation of China (CN) (Grant Nos. NSFC 42041007).}
